---
title: "farm_profile_2020"
author: "Mihkail Cornell"
date: "2020-10-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidymodels)
library(tidyr)
library(tidyverse)
library(stringr)
library(dplyr)
library(lubridate)
library(ggplot2)
library(ggrepel)

farm_profiles <- read_csv("farm_profiles.csv")

# =IF(OR(N16<0.05),  IF(N16 < 0.01, CONCATENATE(M16,"**"), CONCATENATE(M16,"*")), M16)
```


```{r}

farm_geo_sites <-
  farm_profiles %>%
  select(`Collection Date`, `GPS Long`, `GPS Lat`, Municipality, Barangay) %>%
  mutate(year_collect = year(mdy(`Collection Date`))) %>%
  group_by(year_collect, Municipality, Barangay)

write.csv(farm_geo_sites, "Farm Locations with GPS.csv")


farm_profile_for_map <- read_csv("../farm_profile_for_map.csv") %>% na.omit()
write.csv(farm_profile_for_map, "../farm_profile_googlemap.csv")


farm_profile_for_map %>%
  select(Province, Municipality, Barangay) %>%
  group_by(Province, Municipality) %>%
  count()
```


```Farm profile 2020 summary```
```{r}
farm_profile_2020 <-
  farm_profiles %>%
  mutate(collection_date = mdy(`Collection Date`)) %>%
  filter(year(mdy(`Collection Date`)) == "2020")

leyte_farm_2020 <- 
  farm_profile_2020 %>%
  filter(Province == "Leyte") %>%
  mutate(Farmer = paste(`Farmer First name`, `Farmer Last name`)) %>%
  select(Province, Municipality, Barangay, Farmer, `GPS Long`, `GPS Lat`)

so_leyte_farm_2020 <- 
  farm_profile_2020 %>%
  filter(Province == "Southern Leyte") %>%
  mutate(Farmer = paste(`Farmer First name`, `Farmer Last name`)) %>%
  select(Province, Municipality, Barangay, Farmer, `GPS Long`, `GPS Lat`)

samar_farm_2020 <- 
  farm_profile_2020 %>%
  filter(Province == "Samar") %>%
  mutate(Farmer = paste(`Farmer First name`, `Farmer Last name`)) %>%
  select(Province, Municipality, Barangay, Farmer, `GPS Long`, `GPS Lat`)


# farmers_2020 <-
#   leyte_farm_2020 %>% 
#   full_join(so_leyte_farm_2020)
#   
# write.csv(farmers_2020, "report_2020/Farmer's 2020 Profiles.csv")

  
```



```{r}
# Land Tenure
land_tenure_count <-
  farm_profile_2020 %>%
  group_by(`Land Tenure`) %>%
  mutate(land_tenure = `Land Tenure`) %>%
  count(land_tenure)

land_tenure_count %>%
  arrange(desc(n)) %>%
  mutate(prop = n / (sum(land_tenure_count$n) * 50)) %>%
  mutate(ypos = cumsum(prop) - 1.05 * prop) %>%
  ggplot(aes(x = "", y = n, fill = reorder(land_tenure, n))) + 
  geom_bar(stat="identity", width = 0.5) +
  coord_polar("y") + 
  theme_void() +
  # theme(legend.position="none") +
  geom_text(aes(x = 1.1, y = n * 0.55 + c(0, cumsum(n)[-length(n * 5)]), 
                label = n), color = "black", size = 5) +
  geom_text(aes(y = n * 0.5 + c(0, cumsum(n)[-length(n)]), 
                label = sprintf("(%s)", percent(n/sum(land_tenure_count$n)))), 
            color = "black", size = 4) +
  labs(title = "Pie Graph on Ownership of Land - 2020 Farmer's Profile",
       fill = "Types of Ownership") + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
ggsave(path = "../farm_profile_2020", filename = "Types of Ownership of Land.png")

```

```{r}
# Topography
topography_count <-
  farm_profile_2020 %>%
  group_by(Topography) %>%
  mutate(topography = Topography) %>%
  count(topography)

topography_count %>%
  arrange(desc(n)) %>%
  mutate(prop = n / (sum(topography_count$n) * 50)) %>%
  mutate(ypos = cumsum(prop) - 1.05 * prop) %>%
  ggplot(aes(x = "", y = n, fill = reorder(topography, n))) + 
  geom_bar(stat="identity", width = 0.5) +
  coord_polar("y") + 
  theme_void() +
  # theme(legend.position="none") +
  geom_text(aes(x = 1.09, y = n * 0.55 + c(0, cumsum(n)[-length(n * 5)]), 
                label = n), color = "black", size = 5) +
  geom_text(aes(y = n * 0.4 + c(0, cumsum(n)[-length(n)]), 
                label = sprintf("(%s)", percent(n/sum(topography_count$n)))), 
            color = "black", size = 4) +
  labs(title = "Topography Distribution - 2020 Farmer's Profile",
       fill = "Types of Topography") + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) 
ggsave(path = "../farm_profile_2020", filename = "Types of Topography.png")

```

```{r}
# Soil Texture
soil_texture_count <-
  farm_profile_2020 %>%
  group_by(`Soil Texture`) %>%
  mutate(soil_texture = `Soil Texture`) %>%
  count(soil_texture)

soil_texture_count %>%
  arrange(desc(n)) %>%
  mutate(prop = n / (sum(soil_texture_count$n) * 50)) %>%
  mutate(ypos = cumsum(prop) - 1.05 * prop) %>%
  ggplot(aes(x = "", y = n, fill = reorder(`Soil Texture`, n))) + 
  geom_bar(stat="identity", width = 0.5) +
  coord_polar("y") + 
  theme_void() +
  geom_label_repel(aes(y = n * 0.65 + c(0, cumsum(n)[-length(n)]), 
                label = sprintf("%s (%s)", n, percent(n/sum(soil_texture_count$n)))), 
                color = "black", size = 4, nudge_x = 0.35, show.legend = FALSE) +
  labs(title = "Soil Texture - 2020 Farmer's Profile",
       fill = "Types of Soil Texture") + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) 
ggsave(path = "../farm_profile_2020", filename = "Types of Soil Texture.png")
```

```{r}
# Previous Crop
```

```{r}
# Adjacent Crop
```

```{r}
# Cropping Pattern
```

```{r}
# Source of Planting Materials
material_sources_count <-
  farm_profile_2020 %>%
  mutate(material_sources = `Source of Planting Materials`) %>%
  count(material_sources)

material_sources_count %>% 
  mutate(supplier = case_when(str_detect(material_sources, "([Aa]grivet)") ~ "Agrivet",
                              str_detect(material_sources, "(Agroman)") ~ "Agroman",
                              str_detect(material_sources, "(BCCI)") ~ "BCCI",
                              str_detect(material_sources, "LGU([-, ])*[A-Za-z]* | PAGSO | \\bLGU\\b") ~ "LGU",
                              str_detect(material_sources, "(DA)") ~ "DA",
                              str_detect(material_sources, "[Nn]eighbo[u]r") ~ "Neighbor",
                              str_detect(material_sources, "Owne[rd]") ~ "Owned",
         TRUE ~ material_sources))
```

```{r}
# Crop Stage
```

```{r}
# Planting Distance
```

```{r}
# Fertilizer Application Level
fertilizer_level_count <-
  farm_profile_2020 %>%
  group_by(`Fertilizer Application Level`) %>%
  mutate(fertilizer_level = `Fertilizer Application Level`) %>%
  count(fertilizer_level)


fertilizer_level_count %>%
  arrange(desc(n)) %>%
  mutate(prop = n / (sum(fertilizer_level_count$n) * 50)) %>%
  mutate(ypos = cumsum(prop) - 1.05 * prop) %>%
  ggplot(aes(x = "", y = n, fill = reorder(`Fertilizer Application Level`, n))) + 
  geom_bar(stat="identity", width = 0.5) +
  coord_polar(theta = "y") + 
  theme_void() +
  geom_text(aes(y = n * 0.5 + c(0, cumsum(n)[-length(n)]), 
                label = sprintf("%s (%s)", n, percent(n/sum(fertilizer_level_count$n)))), 
            color = "black", size = 4.8) +
  labs(title = "Fertilizer Application Level - 2020 Farmer's Profile",
       fill = "Types of Fertilizer Application Level") + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
ggsave(path = "../farm_profile_2020", filename = "Types of Fertilizer Application Level.png")
```





```Summaries for Maam Lut``
```{r}
library(datawizard)

summary_profiles <- 
  farm_profiles %>%
  mutate(collection_date = mdy(`Collection Date`),
         year = year(mdy(`Collection Date`)),
         month = month(mdy(`Collection Date`))) 

summary_profiles_2023 <- 
  summary_profiles %>%
  filter(year == "2023") %>%
  select(year, Province, Municipality, FarmID, `Fertilizer Application Level`, `Corn Type`) %>%
  group_by(year, Province, Municipality) 

summary_profiles_2020 <- 
  summary_profiles %>%
  filter(year == "2020") %>%
  select(year, Province, Municipality, FarmID) 


summary_profiles_2021 <- 
  summary_profiles %>%
  filter(year == "2021")  %>%
  select(year, Province, Municipality, FarmID) %>%
  group_by(year, Province, Municipality) %>%
  count()


summary_profiles_2022 <- 
  summary_profiles %>%
  filter(year == "2022") %>%
  select(year, Province, Municipality, FarmID) %>%
  group_by(year, Province, Municipality) %>%
  ungroup() 

summary_farm_profiles <-
  summary_profiles_2020 %>%
  full_join(summary_profiles_2021) %>%
  full_join(summary_profiles_2022) %>%
  full_join(summary_profiles_2023)
  

write.csv(summary_farm_profiles, "Summary Farm Profiles.csv")
write.csv(summary_profiles, "Summarized Farm Profiles Year and Month.csv")





summary_profiles_fert <-
  summary_profiles %>%
  select(year, Province, Municipality, `Corn Type`,
         `Fertilizer Application Level`) %>%
  distinct()


unique_fert_farm_profile_summary <-
  summary_profiles_fert %>%
    group_by(year, Province, Municipality) %>%
    count()

write.csv(unique_fert_farm_profile_summary, "Farm Profiles Overall Summary.csv")
  

summary_profiles %>%
  filter(year == "2020") %>%
  select(year, Province, Municipality, `Corn Type`,
         `Fertilizer Application Level`) %>% View()

summary_profiles %>%
  filter(year == "2020") %>%
  select(year, Province, Municipality, `Corn Type`,
         `Fertilizer Application Level`) %>%
  group_by(year, Province, Municipality, `Corn Type`,
         `Fertilizer Application Level`) %>%
  count() %>% View()


summary_profiles %>%
  filter(year == "2021") %>%
  select(year, Province, Municipality, `Corn Type`,
         `Fertilizer Application Level`) %>%
  group_by(year, Province, Municipality, `Corn Type`,
         `Fertilizer Application Level`) %>%
  count() %>% View()

summary_profiles %>%
  filter(year == "2022") %>%
  select(year, Province, Municipality, `Corn Type`,
         `Fertilizer Application Level`) %>%
  group_by(year, Province, Municipality, `Corn Type`,
         `Fertilizer Application Level`) %>%
  count() %>% View()

summary_profiles %>%
  filter(year == "2023") %>%
  select(year, Province, Municipality, `Corn Type`,
         `Fertilizer Application Level`) %>%
  group_by(year, Province, Municipality, `Corn Type`,
         `Fertilizer Application Level`) %>%
  count() %>% View()
```


```{r}
summary_profiles_2021_1st_cropping <- 
  summary_profiles %>%
  filter(year == "2021",
         month %in% c(2, 3, 4))  %>%
  select(year, `Date Planted`, Province, Municipality, `Corn Type`,
         `Fertilizer Application Level`) %>%
  group_by(year, Province, Municipality, `Corn Type`,
         `Fertilizer Application Level`)



summary_profiles_2021_2nd_cropping <- 
  summary_profiles %>%
  filter(year == "2021",
         month %in% seq(5, 10))  %>%
  select(year, `Date Planted`, Province, Municipality, `Corn Type`,
         `Fertilizer Application Level`) %>%
  group_by(year, Province, Municipality, `Corn Type`,
         `Fertilizer Application Level`)



summary_profiles_2022_1st_cropping <- 
  summary_profiles %>%
  filter(year == "2022",
         month %in% c(2, 3, 4))  %>%
  select(year, `Date Planted`, Province, Municipality, `Corn Type`,
         `Fertilizer Application Level`) %>%
  group_by(year, Province, Municipality, `Corn Type`,
         `Fertilizer Application Level`)



summary_profiles_2022_2nd_cropping <- 
  summary_profiles %>%
  filter(year == "2022",
         month %in% seq(5, 10))  %>%
  select(year, `Date Planted`, Province, Municipality, `Corn Type`,
         `Fertilizer Application Level`) %>%
  group_by(year, Province, Municipality, `Corn Type`,
         `Fertilizer Application Level`)


write.csv(summary_profiles_2021_1st_cropping, "2021 First Cropping.csv")
write.csv(summary_profiles_2021_2nd_cropping, "2021 Second Cropping.csv")
write.csv(summary_profiles_2022_1st_cropping, "2022 First Cropping.csv")
write.csv(summary_profiles_2022_2nd_cropping, "2022 Second Cropping.csv")



```


















